A Survey on Ordered Binary Decision Diagrams

### 2015-09-11 paper.tex
Add subsection Efficient Data Structures and Garbage Collection
Add hash table data structure

@@

>>>>

\subsection{Efficient Data Structures}
\label{subsec:efficient-data-structures}

\paragraph*{Hash Table}
\mbox{} % workaround to get line break after paragraph

Hash tables maintain \textit{key}-\textit{value}-pairs, returning the associated
value for a given key in (amortized) constant time~\cite{BRACE90}.

This is especially useful to refine \textit{Apply} in order to guarantee the time
complexity of $O\left(|V_{f_1}| \cdot |V_{f_2}|\right)$. Using a hash table to
match pairs of nodes ($n_1$, $n_2$) to a single node $m$, \textit{Apply} avoids
making multiple recursive calls to equivalent pairs of nodes and thus avoids
computing equivalent subgraphs multiple times. Therefore, before computing a
subgraph, \textit{Apply} checks whether an entry is present for the given pair
of nodes. If so, the associated value $m$ is used instead of computing the
subgraph~\cite{BRYANT86, BRYANT92}.

Moreover, hash tables are useful to generate a reduced graph directly from some
operations by maintaing a hash table associating triples
($var(n)$, $lo(n)$, $hi(n)$) with a single nonterminal node $n$. This is done for
each nonterminal node $n$ generated while executing the
operation~\cite{BRYANT92}.
\tbr

@@

\subsection{Garbage Collection}
\label{subsec:garbage-collection}
